Tabular Constraint Learning

### 2016-04-29 Paper/ECAI/tabular.tex
Edits part 1

The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.
\\\\
\sergey{Can be parallelized by looking at connected components and respecting order}
Most parts of the algorithm could be easily parallelized.
However, \dependencies would impose a partial order in which constraint templates would have to be treated.

@@

Finding candidate groups for a \template~$t$ can be seen as a Constraint Satisfaction Problem (CSP) dependent on the \CSignature of~$t$.
\tias{...such that at least one subgroup satisfies the signature}
For every argument in~$t$ we consider all groups~\groups (or all candidates from a more general constraint) and prune these candidate groups using their types and other requirements imposed by the templates \CSignature, such that those groups or some of their subgroups satisfy the \CSignature.

>>>>

The \ecrank{v_y}{v_x} constraint does not have any dependencies, however in a restricted version without ties groups assigned to $v_y$ would always be a permutation of numbers $1, 2, ..., \textit{length}(v_y)$.
\\\\
Most parts of the algorithm could be easily parallelized.
Every connected component in \dependencies can be learned independently.
Within every component, constraint templates have to be treated respecting the order, i.e. learning the most general ones first.
The generality ordering thus imposes a partial ordering according to which constraint templates must be learned.

@@

Finding candidate groups for a \template~$t$ can be seen as a Constraint Satisfaction Problem (CSP) dependent on the \CSignature of~$t$.
For every argument in~$t$ we consider all groups~\groups (or all candidates from a more general constraint) and prune these candidate groups using their types and other requirements imposed by the templates \CSignature, such that a group~$G \in \groups$ is selected if there is at least one subgroup~$G' \subseteq G$ that satisfies the \CSignature.
